Normalized expressions

### 2021-08-10 analysis/normalized.Rmd
Tags with the non necessary evals

```{r, eval=dataset_name == "package", eval = FALSE}
manual_value_necessary <- read_csv(path(params$base_dir, "non-necessary-value-evals.csv"), col_types = cols(src_ref = col_character(), necessary = col_logical()))

>>>>

```{r, eval=dataset_name == "package"}
manual_value_necessary <- read_csv(path(params$base_dir, "non-necessary-value-evals.csv"), col_types = cols(src_ref = col_character(), necessary = col_logical()))
